Dynamic Load Balancing for\\Heterogeneous Systems

### 2011-12-05 paper/paper.tex
Included more figures.

The dynamic load-balancing scheme will still not guarantee optimal performance.
Within a work chunk, a single long-running workgroup can hold up the entire device,
not allowing other kernels to execute on open SMs.  This creates and issue where the
size of the work chunks should be considered.  One one hand, larger work chunks can
provide for better performance for each device, as it will allow more workgroups to
hide the cost of a long-running workgroup.  However, large chunk sizes can reduce
the granularity of load-balancing between the devices.

@@

%\begin{figure}[t]
%\centering
%\includegraphics[width=3.0in]{reduce_static_fused}
%\caption{Reduction Benchmark with Varied Execution Ratio}
%\label{fig:reduce_static_fused}
%\end{figure}

%\begin{figure}[t]
%\centering
%\includegraphics[width=3.0in]{vector_static_fused}
%\caption{Vector Add Benchmark with Varied Execution Ratio}
%\label{fig:vector_static_fused}
%\end{figure}

%\begin{figure}[t]
%\centering
%\includegraphics[width=3.0in]{vector_plus_static_fused}
%\caption{Vector Add+ Benchmark with Varied Execution Ratio}
%\label{fig:vector_plus_static_fused}
%\end{figure}

%Finally, consider Figures \ref{fig:reduce_static_fused}, \ref{fig:vector_static_fused},
%and \ref{fig:vector_plus_static_fused}. In each, the runtim for both the CPU and GPU are
%shown with a 16~MB problem size.  Additionally, a variety of static execution ratios are
%shown between 0.1\% and 99.9\%.  In every benchmark, none of the execution ratios were
%able to achieve a better time than just the GPU.

>>>>

The dynamic load-balancing scheme will still not guarantee optimal performance.
Within a work chunk, a single long-running workgroup can hold up the entire device,
not allowing other kernels to execute on open SMs.  This creates and issue where the
size of the work chunks should be considered.  One one hand, larger work chunks can
provide for better performance for each device, as it will allow more workgroups to
hide the cost of a long-running workgroup.  However, large chunk sizes can reduce
the granularity of load-balancing between the devices.  Alternatively, smaller chunk
sizes alleviates the problem of one device receiving a disproportionate amount of the
work, but can increase scheduling overhead by increasing contention for the shared
variable which tracks the remaining workload.

@@

\begin{figure}[t]
\centering
\includegraphics[width=3.0in]{reduce_static_fused}
\caption{Reduction Benchmark with Varied Execution Ratio}
\label{fig:reduce_static_fused}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3.0in]{vector_static_fused}
\caption{Vector Add Benchmark with Varied Execution Ratio}
\label{fig:vector_static_fused}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=3.0in]{vector_plus_static_fused}
\caption{Vector Add+ Benchmark with Varied Execution Ratio}
\label{fig:vector_plus_static_fused}
\end{figure}

%Finally, consider Figures \ref{fig:reduce_static_fused}, \ref{fig:vector_static_fused},
%and \ref{fig:vector_plus_static_fused}. In each, the runtime for both the CPU and GPU are
%shown with a 16~MB problem size.  Additionally, a variety of static execution ratios are
%shown between 0.1\% and 99.9\%.  In every benchmark, none of the execution ratios were
%able to achieve a better time than just the GPU.

Finally, consider Figure \ref{fig:vector_static_fused}, where the overall runtime
for the static load balancer is compared against both the CPU-only and GPU-only
runtimes for 0.1\%, 1\%, 10\%, 25\%, 50\%, 75\%, 99\%, and 99.9\% static data
ratios for the 16~MB vector add benchmark.  Figures \ref{fig:reduce_static_fused}
and \ref{fig:vector_plus_static_fused} show similar results for the reduction and
vector add+ benchmarks.  In these benchmarks, the downward trend as more data is
executed on the GPU becomes more evident.  What's also interesting is that the
static load balancer actually performs worse than the CPU-only case when only a
small amount of the data ($\leq$1\%) is executed on the CPU in the reduction and
vector add benchmarks.
